Post MCMCglmm analyses

### 2021-04-09 Analysis/06-post_mcmcglmm_analyses.Rmd
Update 06-post_mcmcglmm_analyses.Rmd

Or without all the points n stuff

>>>>

Note that the major axes look slightly off for some of the ellipses.
I think this is due to the difference in aspect ratio in both plots that exagerates vertical positions and deforms the ellipses:

```{r}
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)",
     main = "Major axes of the ellipses\n(aspect ratio = 1)",xlim = c(-1.5, 1.5), ylim = c(-1.5, 1.5))
plot.ellipses(covar_matrices, centre = "level",
              col = c("grey",colour_vector),
              add = TRUE)
plot.all.axes(level_centred_major_axes,
         col = c("grey",colour_vector),
         add = TRUE)
```

This is an example with just the major axes (projected in 2D):
